Sparse Function Space Representation of Neural Networks for Exploration and Retention

### 2023-05-10 paper/main.tex
Minot

\begin{figure}[t!]
  \centering
  % Set figure size
  \setlength{\figurewidth}{.31\textwidth}
  \setlength{\figureheight}{\figurewidth}
  %
  \begin{tikzpicture}[outer sep=0,inner sep=0]

@@

     % The arrow
     \tikzstyle{myarrow} = [draw=black!80, single arrow, minimum height=12mm, minimum width=2pt, single arrow head extend=4pt, fill=black!80, anchor=center, rotate=0, inner sep=5pt, rounded corners=1pt]
     \node[myarrow] (first-arr) at ($(banana-nn)!0.5!(banana-nn2svgp)$) {};
     \node[myarrow] (second-arr) at ($(banana-nn2svgp)!0.5!(banana-update)$) {};

     % Arrow labels
     \node[font=\scriptsize,color=white] at (first-arr) {nn2svgp};
     \node[font=\scriptsize,color=white] at (second-arr) {new data};

@@

  \end{tikzpicture}
  \caption{Teaser figure goes here.}
  \label{fig:banana}  
\end{figure}

@@

>>>>

\begin{figure}[t!]
  \centering
  % Set figure size
  \setlength{\figurewidth}{.31\textwidth}
  \setlength{\figureheight}{\figurewidth}
  %
  % Colours
  \definecolor{C0}{HTML}{DF6679}
  \definecolor{C1}{HTML}{69A9CE}
  %
  \begin{tikzpicture}[outer sep=0,inner sep=0]

@@

     % The arrow
     \tikzstyle{myarrow} = [draw=black!80, single arrow, minimum height=14mm, minimum width=2pt, single arrow head extend=4pt, fill=black!80, anchor=center, rotate=0, inner sep=5pt, rounded corners=1pt]
     \node[myarrow] (first-arr) at ($(banana-nn)!0.5!(banana-nn2svgp)$) {};
     \node[myarrow] (second-arr) at ($(banana-nn2svgp)!0.5!(banana-update)$) {};

     % Arrow labels
     \node[font=\scriptsize\sc,color=white] at (first-arr) {nn2svgp};
     \node[font=\scriptsize\sc,color=white] at (second-arr) {new data};

@@

  \end{tikzpicture}
  \newcommand{\mycircle}{\protect\tikz[baseline=-.5ex]\protect\node[circle,inner sep=2pt,draw=black,fill=C0,opacity=.5]{};}
  \newcommand{\mysquare}{\protect\tikz[baseline=-.5ex]\protect\node[inner sep=2.5pt,draw=black,fill=C1,opacity=.5]{};}
  %
  \caption{Binary classification (\mysquare~vs.~\mycircle)}
  \label{fig:banana}  
\end{figure}

@@

A reference implementation of the methods presented in this paper is currently available as supplementary material and will be made available under the MIT License on GitHub upon acceptance.
